Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
update discussion and future research

## Discussion
Our model suggests that there is some weak evidence that with increasing temperature, the reproductive number R decreases. The effect of relative humidity on the reproductive number is much less conclusive. As we only used data from Italy in our model building, there is a limited range of weather information than we would like to have.

@@

Look into statistical simulation models which consider intercity travel and geographic proximity.

>>>>

## Discussion
The posterior estimates of our model suggest that there is some weak evidence that with increasing temperature, the reproductive number R decreases. The effect of relative humidity on the reproductive number is much less conclusive. As we only used data from Italy in our model building, there is a limited range of weather information than we would like to have. With no access to line-list data to estimate the serial interval number ourselves, our estimated reproductive number R is limited by the accuracy of the serial interval number we used. The estimated R values tend to have wide confidence interval in the beginning dates due to the imported cases in the beginning and the lack of testing. Overall, our model does a good job estimating the reproductive number R in various provinces with high confidence level and provides valuable information for policy makers.

@@

Look into statistical simulation models which consider intercity travel and geographic proximity. It would also be worthwhile to see the sensitivity of our model with different values of serial interval number.
